Toxic Code Snippets on Stack Overflow

### 2018-05-14 cloverflow-tse/cover_letter/cover_letter.tex
Start restructuring the paper.

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{natbib}

@@

\begin{enumerate}
	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects. Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star. We selected SourcererCC with 80\% similarity for this experiment and detected clones between the 101 outdated code snippets and the retrieved GitHub data set. We relied on SourcererCC because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly matched (they contained additional code modifications made by the projects' developers). Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.

	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow. However, the attributions pointed to different posts that the ones we found the outdated code, but containing the same code in the answers. The other 32 cloned snippets were very likely to be a file-level clone from its original projects based on their license header and the Javadoc comments. Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks). Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects. It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.  
	Nevertheless, we decided to report the developers of the two projects regarding the issue. We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop. The issue has been fixed in deeplearning4j. The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base. On the other hand, the bug report in Apache Hive is still unfixed.
	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets because ... developers in the future.}''.
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an empirical study of code cloning between Stack Overflow toxic code snippets and GitHub projects. Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers). This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017). We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey. However, we did find some interesting results and we discussed only the key findings in~Section \ref{#}. We copied the text below.

@@

tho
Thailand's popular technology news and media community in Thailand called
\texttt{blognone.com}, the University of Molise in Italy where the third author
works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. We received answers from 89 participants. Two participants never
copy code from Stack Overflow so we analysed the answers of the remaining 87
participants. The key findings are as follows.

@@

For the detective measure, while checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones. As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints with human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow. Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time. Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects. The form should include the origin of the code snippet and its original license.

@@

You are right. We mainly study the online code clones and established their existence. However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning. 
Moreover, the term code cloning is not well known outside the code cloning community, so we decided not to use the term in the title.

@@

Nevertheless, since this is a very interesting suggestion. We also performed an investigation of the 101 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet. We include the result of this investigation in the RQ regarding outdated code (RQ?). We found that, out of 101 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment). Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data. We added this discussion in the RQ\FIXME{?}.

@@

We appreciate the comments. We have refined our definition of toxic code snippets in the paper to:

\FIXME{Is this ok?}~``Toxic code snippets mean cloned code snippets that
are harmful for reuse due to (1) being outdated and containing bugs or (2) violating their original software license. They are two ramifications of code cloning
including bug propagation~\citep{Bellon2007}
and software license violations~\citep{An2017}.
Toxic code snippets can occur in software projects or programming Q\&A websites, such
as Stack Overflow.
This study focuses on toxic code snippets that occur on Stack Overflow and how they occur.''

@@

Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 101 posts containing outdated code snippets as accepted answers. We discussed the findings in the relevant RQ. \FIXME{Add the findings.}

@@

Good point. Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming. We have performed the check as you suggested by checking the commit message of each change that make the code outdated and included the findings in RQ?. \FIXME{Add the findings.}

@@

Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow. We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not. The check was performed on 6 May 2018, approximately 2 years after the snapshot was created. Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users. For the 101 outdated answers, we found that one answer was deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue. 
For the xxx license-incompatible answers, \FIXME{add the results}.
We included this discussion in RQ\FIXME{?} and RQ\FIXME{?}.

>>>>

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{booktabs} % For formal tables

@@

\begin{enumerate}
	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects. Hence, we have performed a study of code clone detection between our reported outdated code snippets on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star. We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code). Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.

	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow. However, the attributions pointed to different posts than the ones we found, but containing the same code in the answers. The other 32 cloned snippets were very likely to be a file-level clone from its respective original project (e.g. JFreeChart, JUnit, Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks). Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects. It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.  
	Nevertheless, we decided to report the developers of the two projects regarding the issue. We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop. The issue has been fixed in deeplearning4j. The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base. On the other hand, the bug report in Apache Hive is still unfixed.
	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an empirical study of code cloning between Stack Overflow toxic code snippets and GitHub projects. Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers). This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017) and the full results are reported in our technical report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey. However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1 \ref{#}. We copied the text below.

@@

We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via various channels: social media post (Facebook),
Thailand's popular technology news and media community in Thailand called
\texttt{blognone.com}, the University of Molise in Italy where the third author
works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. We received answers from 89 participants. Two participants never
copy code from Stack Overflow so we analysed the answers of the remaining 87
participants. The key findings are as follows.

@@

For the detective measure, while checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones. As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints based on human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow. Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time. Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects. The form should include the origin of the code snippet (possibly as a GitHub url) and its original license. Using this manually established links at posting time, we can then automate the process of checking for outdated code.

@@

You are right. We mainly study the online code clones and established their existence. However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning. 
Moreover, the term code cloning is not well known outside the code cloning community. Code clones are called differently in each research community or in practice, such as duplicated code, copy-and-paste code, code reuse, software similarity or software redundancy. So, we decided not to use the term in the title.

@@

Nevertheless, since this is a very interesting suggestion. We also performed an investigation of the 101 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet. We include the result of this investigation in the RQ regarding outdated code (RQ?). We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment). Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data. None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users. We added this discussion in the RQ\FIXME{?}.

@@

We appreciate the comments. We have refined our definition of toxic code snippets in the paper by adapting from Israel Gat's definition~\citep{toxiccode} which links toxic code to technical debt, i.e.~``a metaphor reflecting technical compromises that can yield short-term benefit but may hurt the long-term health of a software system''~\citep{Li2015}. The new definition of toxic doe snippets are as follows.

``Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated or (2)~violating their original software
license. Outdated code snippets
can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 100 posts containing outdated code snippets as accepted answers. We found that there were 34 posts which contains newer answers. Regarding the number of votes, there were 5 posts which contained other answers with a higher number of votes than the outdated answer. Ninety-nine out of the one hundred outdated code were still marked as accepted answers. 
This discussion of the findings is added to the the RQ\FIXME{?}.

@@

Good point. Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming. We have performed the check as you suggested by checking the commit message of each change that make the code outdated. The findings are discussed below and are included in the RQ\FIXME{?}.

We looked through the commit history of 100 outdated code snippets and summarised the reasons of code updates. We carefully read the commit messages and/or used the bug IDs in the commit messages to obtain more information from the bug report systems. We summarised the reasons of code changes into 6 groups as shown in the table below.

\begin{table}
	\centering
	\begin{tabular}{llr}
		\toprule
		Reason & Detail & Amount \\
		\midrule
		Enhancement & Add features or update existing features & 64 \\
		Deprecation & Delete dead or deprecated code & 15 \\
		Bug & Fix bugs & 10 \\
		Refactoring & Refactor code for better design & 6 \\
		Coding style & Update code to conform to a style guideline & 3 \\
		Data change & Change code due to changing of the data & 2 \\
		\bottomrule
	\end{tabular}
	\caption{Reasons of code changes in 100 outdated code snippets}
\end{table}

The majority of the changes are due to code enhancement. There are 64 changes for software enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs. Fifteen changes are for removal of dead or deprecated code such as SQL connection code in Hibernate. Ten changes are made to fix bugs in the software (e.g.~array reference, race condition, wrong field access, \texttt{NullPointerException}). There are 6 changes for code refactoring, 3 changes for updating coding styles using an automated tool or manually, and 2 changes that are caused by the change of data format.

@@

Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow. We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not. The check was performed on 6 May 2018, approximately 2 years after the snapshot was created. Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users. From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue. 
We included this discussion in RQ\FIXME{?}.
